An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-26 scagnostics.Rmd
Summary table added.

>>>>

## Summary

Our results can be summarised by comparing

- scagnostics indices:
    - advantages: scaling with larger datasets thanks to binning, set of index functions covering different types of interesting structures
    - disadvantage: noisy, requires good optimisation algorithm, stringy too noisy to be used as index
- splines2D:
    - advantages: fast to compute, also considering scaling with larger data sets, efficient in detecting functional relations, typically smooth behaviour (but we have seen some exceptions)
    - disadvantage: not general, highly not rotation invariant
- dcor2D:
    - advantages: smoothly changing, sensitive to general structure
    - disadvantage: slow if computed without binning, large sensitivity to noise compared to MIC/TIC (example: low values obtained for the circle view of the pipe), sensitive to rotation
    - NOTE: I have not tested this much, should probably add binned version to timing plot
- MINE (MIC, TIC):
    - advantages: general, good discrimination even with noisy structures
    - disadvantages: slow to compute, noisy for small datasets, TIC sensitive to rotation

\begin{table}
\begin{center}
\caption{Summary}
\label{tab:summary}
\begin{tabular}{|l|c|c|c|c|}
\hline
Index & smooth & rotation invariant & fast & general \\
\hline
Convex & ! & ! & \checkmark & ! \\
Skinny & ! & ! & \checkmark & ! \\
Stringy & $\times$ & ! & \checkmark & ! \\
\hline
splines2D & \checkmark & $\times$ & \checkmark & ! \\
dcor2D & \checkmark & $\times$ & ! & ! \\
\hline
MINE & ! & ! & ! & \checkmark\\
\hline
\end{tabular}
\end{center}
\end{table}
